---
title: "week9_pdf"
author: "Mathi Manavalan"
date: "3/21/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Studio API

## Libraries
```{r libraries, message=FALSE}
library(tidyverse)
library(lubridate)
library(ggplot2)

```

## Data Import
```{r data import, message=FALSE, warning=FALSE}
week9_tbl <- as.tibble(read_csv(file = "../data/week3.csv")) %>% 
  mutate(timeStart = ymd_hms(timeStart), timeEnd = ymd_hms(timeEnd)) %>%  
  mutate(condition = factor(condition, levels = c("A", "B", "C"), 
                            labels = c("Block A", "Block B", "Control")), 
         gender = factor(gender, levels = c("M", "F"), labels = c("Male", "Female"))) %>% 
  mutate(avg15 = (q1 + q2 + q3 + q4 + q5)/5, avg610 = (q6 + q7 + q8 + q9 + q10)/5)
```

Cleaning steps done

* imported data as a tibble
* formatted date and time into appropriate variable types
* formatted condition and gender into appropriately labeled factors
* created two new columns of data
  + column of average of scores on questions Q1-Q5
  + column of average of score on questions Q6-Q10

## Visualization

```{r visualization, echo=FALSE, message=FALSE, include=TRUE}

ggplot(week9_tbl, aes(x=avg15, y= avg610)) + 
  geom_jitter() +
  labs(x = "Mean scores of Q1 - Q5", y = "Mean scores of Q6 - Q10") +
  geom_smooth(method = "lm", se = FALSE)


```

The above plot displays a scatterplot of the average scores of participants in questions Q1 through Q5 and the average scores of same participants in questions Q6 through Q10.

## Analysis

```{r analysis}
analysis <- summary(lm(week9_tbl$avg610 ~ week9_tbl$avg15))
analysis
```
The correlation was `r analysis$r.squared` (p<.05), which is not statistically significant.